The paper on blockchain front-running

### 2018-09-25 frontrunning/Latex/sections/paper.tex

In the cryptographic literature, front-running attacks are modelled by allowing a `rushing' adversary to interact with the protocol. In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running. See \eg \textblue{the Bitcoin Backbone~\cite{garay2015bitcoin}} and Hawk~\cite{kosba2016hawk}.

@@

\textblue{Although sealed auction method is used in ENS implementation, the normal workflow uses \texttt{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to outbid the initial sealed bid. By doing so the front-runner invalidates the original bid and hence registers the domain name himself.}

>>>>

In the cryptographic literature, front-running attacks are modelled by allowing a `rushing' adversary to interact with the protocol. In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running. See \eg~\cite{garay2015bitcoin} and Hawk~\cite{kosba2016hawk}.

@@
